%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-1in}
\addtolength{\evensidemargin}{-1in}
\addtolength{\textwidth}{2in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Defining a highlight-color
\definecolor{highlightColor}{rgb}{0, 0, 0}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large \color{highlightColor}
}{}{0em}{}[\color{highlightColor}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & #2 \\
      #3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeResearchItem}[3]{
  \vspace{-1pt}\item\small{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}
    #3
  }
  \vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=12pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\textbf{\Huge \color{highlightColor} Charles Yu} \\
108 Eddy St Apt 21, Ithaca NY, 14850 \\

\faPhone \hspace{2 pt} 650.862.8697
\hspace{2pt}
\faEnvelope \hspace{2 pt} \href{mailto:charles.yu108@gmail.com}{charles.yu108@gmail.com}
\hspace{2pt}
\faGlobe \hspace{2 pt} \href{http://charlesyu108.github.io/}{charlesyu108.github.io} \\


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {Computer Science,  M.Eng.}{Jan 2019 -- May 2019} \\
      \vspace{5pt}
      \textit{\small Beginning Jan 2019}
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {Computer Science, B.A. -- GPA: 3.826}{Aug 2015 -- Dec 2018} \\
      \vspace{5pt}
      \textit{\small Minor in Asian American Studies; Dean's List 6 semesters}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ab Initio Software}{Lexington, MA}
      {Software Engineering Intern}{Jun 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem {REST-to-DML}
          {Code generation utility that takes a RESTful API service description (Swagger/OpenAPI) and generates service-specific Ab Initio DML code
          to call the described endpoint operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Workday}{Pleasanton, CA}
      {Software Engineering Intern}{May 2017 - Aug 2017}
      \resumeItemListStart
        \resumeItem{Authorization Engine}
          {Designed a role-based access control authorization schema \& built an authorization engine for an internal web service.}
        \resumeItem{Elastic Stack Log Archive}
          {Built proof-of-concept service for remote server log aggregation, log searching, and log-metric visualization using elastic stack.}
      \resumeItemListEnd

    \resumeSubheading
      {Knodemy}{Livermore, CA}
      {iOS Development Intern}{Jun 2016 - Aug 2016}
      \resumeItemListStart
        \resumeItem{K'nnect Mobile App}
          {iOS app to connect students with mentors at hackathons.  Implemented chat service, newsfeed, user-registration, authentication, and Firebase integration.}
      \resumeItemListEnd
      \vspace{-8pt}
  \resumeSubHeadingListEnd

%-------------RESEARCH--------------
\section{Research}
  \resumeSubHeadingListStart
    \resumeResearchItem {Cornell Systems Lab: Blockchain Sharding Solutions} {Feb 2018 - Present}
      {On-chain sharding solution built on Bitcoin-NG with Emin G{\"u}n Sirer, Soumya Basu, and Kai Mast}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects \& Portfolio Pieces}
  \resumeSubHeadingListStart
    \resumeSubItem {peoplethink -- \href{http://peoplethink.herokuapp.com/} {\faGlobe \hspace{1pt} peoplethink.herokuapp.com} }
      {Ad-hoc information retrieval system for exploring the opinions andsentiments of niche communities on any topic imaginable.  Built on Q\&A pairs from the top 1000 Reddit /r/IAMA postsof all time (as of March 2017) }
    \resumeSubItem {The Wine Network -- \href{http://charlesyu108.github.io/wineviz/} {\faGlobe \hspace{1pt} charlesyu108.github.io/wineviz} }
       {Interactive d3 visualization for exploring wine varietals through a graph network. Varietal similarity determined through analysis of textual review features.}
    \resumeSubItem {AnnouncementBot}
      {GroupMe mass notification and announcement system.}
  \resumeSubHeadingListEnd

%-----------ADDITIONAL-----------------
\section{Addittional}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {\textbf{[Proficient]} Python, JavaScript, OCaml, Java
      \textbf{[Familiar]} Scala, Swift, C, Ab Initio}
    \resumeSubItem{Tools and Frameworks}
      {d3.js, Heroku, Play Framework,
       Flask, Django, scikit-learn, AngularJS, Elastic (ELK) Stack, MongoDB}
    \resumeSubItem{Extracurricular Activities}
      {CS 3110 (Functional Programming) Course Staff -- Fall 2018,
       CS 4300 (Information Retrieval) Course Staff -- Spring 2018,
       Sigma Phi Epsilon, Lifestyle Blogger for the Cornell Daily Sun }
    \resumeSubItem{Interests}
      {Music, Pour-over coffee, Writing, Fishing, Thrifting}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
